Labor Markets and Technological Change: Evidence from Electronic Health Records

### 2021-10-21 Presentations/ThirdYearPaperpres.tex

\usetheme[progressbar=frametitle]{metropolis}
\usepackage{appendixnumberbeamer}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage[scale=2]{ccicons}
\usepackage[style=authoryear]{biblatex}
\bibliography{demo.bib}
\usepackage{pgfplots}
\usepackage{bbm}

@@

\begin{frame}[fragile]{What does this mean for physicians?}
In the short run:
\begin{itemize}
    \item Physicians spend more time entering information into a computer and learning a new software
    \item Physicians have experienced significant burn-out from using and learning EHRs
\end{itemize}

In the long run:
\begin{itemize}
    \item Could make daily tasks easier or harder
    \item Continued loss of autonomy as technology progresses
\end{itemize}

@@

\begin{frame}{Branches of Literature}
\centering
\includegraphics[scale=.5]{graphics/Contribution_litgraphic.PNG}

@@

\begin{frame}{Physician Labor Literature}
\centering
    \includegraphics[scale=.45]{graphics/labor_litgraphic.PNG}
\end{frame}

\begin{frame}{EHR Literature}
    \centering
    \includegraphics[scale=.45]{graphics/EHR_litgraphic.PNG}
\end{frame}

@@

\begin{frame}{Physician's Incentives}
\begin{itemize}
    \item Physician has a choice set of where to work, including multiple hospitals and office-based locations
    \item All physicians I consider work closely with at least one hospital at some point in time
    \item Some proportion of hospitals implement a new technology (an EHR)
    \item How to think about the effect on labor:
    \begin{enumerate}
        \item EHR makes seeing patients easier (or more difficult), thus the number of patients seen increases (or decreases)
        \item EHR imposes a burden with a high cost, so the physician switches to working at an office-based location where they have more control
        \item A senior physician could be tipped to retire early instead of taking on the cost of learning a new technology
    \end{enumerate}
\end{itemize}
\end{frame}

@@

Physician-level Indicator that captures exposure to \textit{any} EHR
\begin{itemize}
    \item With information on shared patients between physicians and hospitals, I limit to physicians working in hospitals
    \item Fraction of hospitals worked with that use an EHR comes from the AHA survey
    \item Similarly, I can capture hospitals that use EHRs for decision making vs. documentation using the AHA Survey IT Supplement 
\end{itemize}

@@

@@

\begin{frame}{Event Studies}
\begin{equation*}
    Y_{it}= \sum_{t=-6}^6 \mathbbm{1}_{\{\text{relative treatment year}_{i}=t\}} + \alpha_t + \delta_{i} + \mathbb{X}_{it}
\end{equation*}

@@

>>>>

\usetheme[progressbar=frametitle]{metropolis}
\usepackage{appendixnumberbeamer}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage[scale=2]{ccicons}
\usepackage[style=authoryear]{biblatex}
\bibliography{demo.bib}
\usepackage{pgfplots}
\usepackage{bbm}
\usepackage{import}
\usepackage{graphics}

@@

\begin{frame}[fragile]{What does this mean for physicians?}
In the short run:
\begin{itemize}
    \item Physicians spend more time entering information into a computer and learning a new software
    \item Physicians have experienced significant burn-out from using and learning EHRs
    \item Loss of autonomy
\end{itemize}

In the long run:
\begin{itemize}
    \item Could make daily tasks easier or harder
    \item Progressing loss of autonomy as technology progresses
\end{itemize}

@@

\begin{frame}{Effect of Health Information Technology}

@@

\begin{frame}{Physician Labor Decisions}

@@

\begin{frame}{Physician's Incentives}
\begin{itemize}
    \item Physician has a choice set of where to work, including multiple hospitals and office-based locations
    \item All physicians I consider work closely with at least one hospital at some point in time
    \item Some proportion of hospitals implement a new technology (an EHR)
    \item How to think about the effect on labor:
    \begin{enumerate}
        \item EHR makes seeing patients easier (or more difficult), thus physician can see more (or less) patients
        \item If the cost of sing an EHR is high enough, the physician can switch to working at an office-based location where they have more control
        \item A senior physician may have incentive to retire early instead of taking on the cost of learning a new technology
    \end{enumerate}
\end{itemize}
\end{frame}

@@

Physician-level Indicator that captures exposure to \textit{any} EHR
\begin{itemize}
    \item With information on shared patients between physicians and hospitals, I limit to physicians who work in at least one hospital at some point in the time frame
    \item Hospital EHR use comes from AHA survey
    \item Similarly, I can capture hospitals that use EHRs for decision making vs. documentation using the AHA Survey IT Supplement 
\end{itemize}

@@

\begin{frame}{Summary Stats}
\centering
    \includegraphics[scale=.7]{Objects/sumstats.pdf}
\end{frame}

\begin{frame}{Physician EHR Use}
    \centering
    \includegraphics[scale=.5]{Objects/sum_stats_year.pdf}
\end{frame}

@@

\begin{frame}{Analysis}

@@

\section{Results}

\begin{frame}[shrink=30]{Total Patients}
\centering
\import{Objects/}{continuous.tex}
\end{frame}

\begin{frame}[shrink=30]{Total Patients}
\centering
\import{Objects/}{continuous_old.tex}
\end{frame}

\begin{frame}[shrink=30]{Working}
\centering
\import{Objects/}{indicator.tex}
\end{frame}

\begin{frame}[shrink=30]{Retirement?}
\centering
\import{Objects/}{indicator_old.tex}
\end{frame}
